Computer Science House By-Laws

### 2016-02-02 bylaws.tex

\bsection{Expenditure Approval}
All House expenditures must be approved by both the Financial Director and the appropriate Director (from whose budget the funds will be drawn). Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures may not exceed one-hundred dollars (\$100). A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
\\* \\*
If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}. At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300). A quorum of one-half the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
\\*\\*
For expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting. This proposal includes the project budget, inventory of required resources, and a timeline for completion.
\\* \\*
If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount. This amount is to be directly subtracted from the general CSH account. 
\\* \\*
Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.

>>>>

\bsection{Expenditure Approval}
All House expenditures must be approved by both the Financial Director and the appropriate Director (from whose budget the funds will be drawn). Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures may not exceed one-hundred dollars (\$100). A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
\\* \\*
If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}. At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300). A quorum of one-quarter the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
\\*\\*
For expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting. This proposal includes the project budget, inventory of required resources, and a timeline for completion.
\\* \\*
If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount. This amount is to be directly subtracted from the general CSH account. 
\\* \\*
Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.
